Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2022-08-01 sports_analytics.Rmd
Corrected the expected value notation.

\begin{equation}
  \mathbb{E}[X | s] = \sum_{X \geq 0} \Pr[X | s] \cdot X\,,
\end{equation}

for any state $s \in S$, where $\Pr[X | s]$ is the probability of scoring $X$ points given that the game is in state $s$ and $S$ is the set of all possible states.

>>>>

\begin{equation}
  \mathbb{E}[X | s] = \sum_{x \geq 0} \Pr[X = x | s] \cdot x\,,
\end{equation}

for any state $s \in S$, where $\Pr[X = x | s]$ is the probability of scoring $x$ points given that the game is in state $s$ and $S$ is the set of all possible states.
